Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
update renv. first par manuscript. update refs

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015]. Studies report for many predator species that populations are often comprised of an assemblage of individuals specialising in different foraging strategies or resources [].

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016]. Indeed, predator populations are often comprised of an assemblage of individuals that specialize in different foraging strategies or resources [@ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017]. Sexual and age related differences are common proximate factors underlying such among-individual variation, while environmental heterogeneity is known as a prevailing external factor [].

*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécxialisation est toujours là!!* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*
